### 2025-10-09 acronyms/acronyms.tex
water
iri
acronyms
rwr
risk index
eo
g7
wrc
bws
acronyms TOP

@@

@@

@@

@@

\newacronym{pi}{PI}{Principal Invesigator}

@@

@@

@@

@@

@@

@@

@@

>>>>

\newacronym{eo}{EO}{Executive Order}

@@

\newacronym{g7}{G7}{Group of Seven}

@@

\newacronym{sca}{SECA}{Simultaneous Evaluation of Criteria and Alternatives}

@@

\newacronym{top}{TOPSIS}{Technique for Order of Preference by Similarity to Ideal Solution}

@@

\newacronym{pi}{PI}{Principal Investigator}

@@

\newacronym{bws}{BWS}{Baseline Water Stress}

@@

\newacronym{ds}{DS}{Drought Severity}
\newacronym{dta}{DTA}{Demand to Available}
\newacronym{edr}{EDR}{External Dependency Ratio}
\newacronym{efr}{EFR}{Environmental Flow Requirements}
\newacronym{ewr}{EWR}{Environmental Water Requirements}

@@

\newacronym{fri}{FRI}{Flood Risk Index}
\newacronym{gr}{GR}{Governance \& Regulation}

@@

\newacronym{rfr}{RFR}{Return Flow Ratio}
\newacronym{rwr}{RWR}{Renewable Water Resource}

@@

\newacronym{ssd}{SS-DTA}{Sectoral and Statistical Demand to Availability}
\newacronym{sv}{SV}{Seasonal Variability}

@@

\newacronym{wrc}{WRCC}{Water Resources Carrying Capacity}

@@

\newacronym{wta}{WTA}{Withdrawl To Availability}
%%%%% energy
\newacronym{iri}{IESRI}{International Energy Security Risk Index}
